Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-13 arxiv/diff_cov.tex
polish section 2/3

Next, we illustrate an interesting phenomenon where adding task one's samples helps task two initially, but hurts eventually.
Consider the limiting estimate on the left hand side of equation \eqref{cor_MTL_error}.
We vary sample ratio $n_1 / n_2$ by fixing $n_2$ and increasing $n_1$.
%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
%We describe a sketch of the proof.
The variance term always reduces as $n_1$ increases.
The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
Furthermore, by calculating the derivative of the bias-variance limits with respect to $n_1$, we obtain the following dichotomy (details omitted).
\begin{enumerate}
	\item When $\frac{2d^2}{d^2 + \sigma^2} < \frac{p}{n_2 - p}$, the prediction loss decreases monotonically as $n_1$ increases.
	\item When $\frac{2d^2}{d^2 + \sigma^2} > \frac{p}{n_2 - p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one positive root for the derivative being zero.
\end{enumerate}

>>>>

Next, we illustrate an interesting phenomenon where adding task one's samples helps task two initially, but hurts eventually.
Consider the limiting estimate on the left hand side of equation \eqref{cor_MTL_error}.
We vary sample ratio $n_1 / n_2$ by fixing $n_2$ and increasing $n_1$.
%As a function of the sample ratio, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ with $n_1$ being zero, and then increases to $d^2$ when $n_1$ goes to infinity.
%We describe a sketch of the proof.
The variance term always reduces as $n_1$ increases.
The bias term always increases as $n_1$ increases, which can be verified by calculating the derivative of the bias term.
Furthermore, by calculating the derivative of the bias-variance limits with respect to $n_1$, we obtain the following dichotomy (details omitted).
\begin{enumerate}
	\item When $\frac{d^2}{\sigma^2} < \frac{p}{2n_2 - 3p}$, the prediction loss decreases monotonically as $n_1$ increases.
	Intuitively, this regime of $d^2$ always helps task two.
	\item When $\frac{d^2}{\sigma^2} > \frac{p}{2n_2 - 3p}$, the limiting estimate always decreases first from $\frac{\sigma^2 p}{n_2 - p}$ (when $n_1 = 0$), and then increases to $d^2$ (when $n_1 \rightarrow \infty$).
	To see this, near the point where $n_1$ is zero, one can verify that bias increases less than the variance decreases, and there is only one critical point for the derivative being zero, which corresponds to the \textit{optimal sample size ratio}.
\end{enumerate}
